Think again?\\ Optimal mental simulation tracks problem difficulty

### 2015-01-28 manuscript.tex
Add new figures
Update figures
Update figures and results, resolve TODOs

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/human-pct-vs-rt.pdf}
        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color). Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.  The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time. \TODO{fix legends} \TODO{right subplot shouldn't be speed vs. accuracy}}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure*}

@@

On average, participants were correct 76.1\% of the time ($N=17686$) and responded that the ball would go in the hole 52.8\% of the time ($N=17686$). There was a significant effect of feedback type on participants' responses ($\chi^2(3)=4477.2, p<0.001$) as well as a significant effect of hole size ($\chi^2(1)=168.6, p<0.001$). Additionally, there was an interaction between feedback type and hole size ($\chi^2(3)=64.469, p<0.001$). Figure \ref{fig:pct-vs-rt} (left subplot) shows responses as a function of feedback type and hole size.

@@

The stimuli were modified versions of those used Experiment 1, with two major differences. First, instead of a wall with a hole in it, there was a paddle of length \TODO{}px that could move up and down the $y$-axis. Second, there was no feedback animation; instead, there was just a single feedback image corresponding to the last frame of the feedback animation. Because there was no feedback animation, there were only 48 stimuli (corresponding to the stimulus presentation animations from Experiment 1), plus the seven instruction trials and eight catch trials.

@@

As in Experiment 1, immediately upon pressing ``space'', the initial stimulus presentation began, after which an occluder appeared. However, unlike Experiment 1, as soon as the occluder appeared, a timer also appeared and begin counting down for \TODO{} seconds. During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed. If the ball was on the paddle, then participants were told, ``You caught the ball!''. If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.'' Participants were then instructed to press ``space'' to continue, at which point the next trial would begin.

@@

We fit the model to people's responses in two steps. First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2. \TODO{explain the procedure by which we did this fitting} Using this procedure, we found the best fitting parameters to be $\sigma_p=31.02$, $\kappa_v=255.60$, $\kappa_m=502850.41$, $\kappa_b=50.42$, and $\sigma_0=167.06$. With these parameters, we find very similar results to those from \citeA{Smith:2013fc} (Figure \TODO{}, left subplot). In particular, we found a correlation of $r=0.94$ \TODO{cis} between the model's predicted means of where the ball would end up and people's average location of the paddle.

@@

We fit $\sigma_{adj}$ and $T$ using a grid search to maximize the correlation between SPRT response times (Equation \ref{eq:rt}) and actual response times in Experiment 1. To compute Equation \ref{eq:rt}, we ran $n=10000$ samples from the model, and from these samples (as well as the $\sigma_{adj}$ adjustment) estimated a truncated normal distribution along the wall with the hole in it. From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole. From this procedure, we found the best fitting parameters to be $\sigma_{adj}=0.7$ \TODO{what is the exact value?} and $T=2$.\footnote{If $\sigma_{adj}=0.7$, then $M=0.49$. How could people be taking fewer than one sample? We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.}

\TODO{what about fitting the coefficients from Equation \ref{eq:rt}?}

Participant responses were well correlated with a SPRT model with $T=1$ ($r=0.81$, 95\% CI [0.77, 0.84]), and slightly less so with a SPRT model with $T=2$ ($r=0.78$, 95\% CI [0.74, 0.81]). There was also a significant correlation with resonse time for the $T=2$ SPRT model as computed with Equation \ref{eq:rt} ($r=0.71$, \TODO{95\% CI []}). Figure \TODO{} shows human responses as a function of the model's responses for $T=2$ (middle subplot) as well as human response times as a function of the model's response times (right subplot).

>>>>

\input{results/params.tex}
\input{results/corrs.tex}

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/hole_empirical_results.pdf}
        \caption{\textbf{Response times as a function of response.} Left subplot: each bar shows the proportion of participants saying that the ball will go in the hole for a particular feedback type ($x$-axis) and hole size (color). Middle subplot: like the left subplot, but the $y$-axis shows bootstrapped logarithmic means of response times. Right subplot: each point corresponds to a different stimulus, feedback type, and hole size.  The $x$-axis is the proportion of participants saying the ball will go in the hole, and the $y$ axis is the logarithmic mean response time.}
        \label{fig:pct-vs-rt}
    \end{center}
\end{figure*}

@@

On average, participants were correct 76.1\% of the time and responded that the ball would go in the hole 52.8\% of the time ($N=17686$). There was a significant effect of feedback type on participants' responses ($\chi^2(3)=4477.2, p<0.001$) as well as a significant effect of hole size ($\chi^2(1)=168.6, p<0.001$). Additionally, there was an interaction between feedback type and hole size ($\chi^2(3)=64.469, p<0.001$). Figure \ref{fig:pct-vs-rt} (left subplot) shows responses as a function of feedback type and hole size.

@@

The stimuli were modified versions of those used Experiment 1, with two major differences. First, instead of a wall with a hole in it, there was a paddle of length 100px that could move up and down the $y$-axis. Second, there was no feedback animation; instead, there was just a single feedback image corresponding to the last frame of the feedback animation. Because there was no feedback animation, there were only 48 stimuli (corresponding to the stimulus presentation animations from Experiment 1), plus the seven instruction trials and eight catch trials.

@@

As in Experiment 1, immediately upon pressing ``space'', the initial stimulus presentation began, after which an occluder appeared. However, unlike Experiment 1, as soon as the occluder appeared, a timer also appeared and begin counting down for 2 seconds. During this time, participants had to move the paddle to try to catch the ball in the position it would be when the timer was up.When the timer countdown finished, the paddle froze at its current location, and the occluder was removed and the full path of the ball revealed. If the ball was on the paddle, then participants were told, ``You caught the ball!''. If the ball was not on the paddle, participants were told ``Oops, you didn't catch the ball.'' Participants were then instructed to press ``space'' to continue, at which point the next trial would begin.

@@

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/model_results.pdf}
        \caption{\textbf{Model vs. human judgments in the paddle task.} \TODO{}}
        \label{fig:model-results}
    \end{center}
\end{figure*}

We fit the model to people's responses in two steps. First, we fit $\sigma_p$, $\kappa_v$, $\kappa_m$, $\kappa_b$, and $\sigma_0$ to particant's responses in Experiment 2 \cite<for details, see>{Smith:2013fc}. Using this procedure, we found the best fitting parameters to be \perr{}, \kapv{}, \kapm{}, \kapb{}, and \sdzero{}. With these parameters, we find very similar results to those from \citeA{Smith:2013fc} (Figure \ref{fig:model-results}, left subplot). In particular, we found a correlation of \PaddleCorr{} between the model's predicted means of where the ball would end up and people's average location of the paddle.

@@

We fit $\sigma_{adj}$ and $T$ using a grid search to maximize the correlation between SPRT response times (Equation \ref{eq:rt}) and actual response times in Experiment 1. To compute Equation \ref{eq:rt}, we ran $n=10000$ samples from the model, and from these samples (as well as the $\sigma_{adj}$ adjustment) estimated a truncated normal distribution along the wall with the hole in it. From this truncated normal, we computed the value of $p$ as the the probability density lying within the region of the hole. From this procedure, we found the best fitting parameters to be \sdadj{} and \threshold{}.\footnote{If \sdadj{}, then $M<1$. How could people be taking fewer than one sample? We suspect that $\sigma_{adj}<1$ because the model actually overestimates the standard deviation; thus, $\sigma_{adj}$ is adjusting for both the inflated uncertainty in the model as well increased certainty in people's judgments on the paddle task.}

Finally, we fit the coefficients from Equation \ref{eq:rt} to people's responses in Experiment 1 using an ordinary least squares regression, where $\mathbb{E}[B]$ and $\mathbb{E}[N\,|\,T,p]$ were computed directly from model simulations. The best-fitting parameters were \betazero{}, which corresponded to the intercept; \betaone{}, which corresponded to the number of samples before making a decision; and \betatwo{}, which corresponded to the number of bounces before making a decision.

Participant responses were well correlated with a SPRT model with \threshold{} (\HoleResponseCorr{}). There was also a significant correlation with resonse time for the \threshold{} SPRT model as computed with Equation \ref{eq:rt} (\HoleRTCorr{}). Figure \ref{fig:model-results} shows human responses as a function of the model's responses for \threshold{} (middle subplot) as well as human response times as a function of the model's response times (right subplot).
